Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-17 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.
progress

\section{Optimization Analysis}
For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The optimization is run under a uniaxial loading condition in the direction parallel non-diagonal elements. In order to maintain reasonable computational complexity, the optimization was run on the unit cell constructed using one dimensional beams with node seeding of at least 1/20 of each beam length. The covariance matrix is initialized uniformly with standard deviation \mf{ADD HERE}.

@@

\section{Parameter Exploration}
Include the graphs showing critical buckling strain as a function of parameters.\\
\mf{Add figures for the diagonal}\\
\mf{Add figure for $\lambda$ exploration}\\
\mf{Write this section}

@@

%\subsection{Analytical Derivation Of Stiffness}
%\subsection{Analytical Derivation of Critical Buckling Strain}
%\subsection{Derivation for }

>>>>

\section{Optimization Analysis}
For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The optimization is run under a uniaxial loading condition in the direction parallel non-diagonal elements. In order to maintain reasonable computational complexity, the optimization was run on the unit cell constructed using one dimensional beams with node seeding of at least 1/20 of each beam length. The covariance matrix is initialized uniformly with standard deviation ($\sigma$) half of the domain space, which are normalized to remain between 0 and 1.

@@

\section{Parameter Exploration}
Include the graphs showing critical buckling strain as a function of parameters.\\
\mf{Add figures for the diagonal}\\
\mf{Add figure for $\lambda$ exploration}\\
\mf{Make sure to include this analysis for both, rectangular cross-section and circular cross-section}\\
\mf{Write this section}
\subsection{Cylindrical Cross Section}
\subsection{Rectangular Cross Section}

@@

\section{Analytical Derivation Of Uniaxial Stiffness}
\mf{Write this section}
%\subsection{Analytical Derivation of Critical Buckling Strain}
